Predicting Covid Data

### 2022-11-30 main.rmd

#Main rmd doc for compiling code at the end

```{r}
library(tidyverse)
```

>>>>

---
title: "Predicting Covid Data"
author: Austin Lackey, Chien Lin and Jin Peng
date: Tuesday, November 6th, 2022
output: powerpoint_presentation
---

## The MonteCarlo Study

- In this study by Ignazio Ciufolini and Antonio Paolozzi, they use a Gauss Error to predict future trends of covid data spread.
- Add more stuff here...

## The Gauss Error function

- The Gauss Error function is widely accepted as a good way to model the spread of covid data, especially in China. By using
the Gauss Error function, we can predict the spread of covid data in the future for other countries.
- $a+b*erf(c*x-d)$

# Australia Simulation

## Australia Simulation
```{r, results=FALSE, echo=FALSE, message=FALSE, warning=FALSE}
library(tidyverse)
library(dplyr)
library(pracma)
data <- read_csv("owid-covid-data.csv")
australia <- data %>% filter(location == "Australia", date > "2020-06-01", date < "2020-12-19")
australia <- subset(australia, select = c(date, total_cases, total_deaths))
australia <- australia %>% mutate(days = 1:n())
minimizedDays <- 70
australiaPre <- australia %>% filter(days < minimizedDays)
cases_Australia <- ggplot(australiaPre, aes(x = date, y = total_cases)) + 
    geom_line() + 
    labs(title = "Total Cases in Australia from 6/1/2020 to 8/9/2020 (70 days)", x = "Date", y = "Total Cases")
fatalities_Australia <- ggplot(australiaPre, aes(x = date, y = total_deaths)) +
    geom_line() + 
    labs(title = "Total Deaths in Australia from 6/1/2020 to 8/9/2020 (70 days)", x = "Date", y = "Total Deaths")
x <- 0:minimizedDays
cases_function_australia <- function(x) 17200+10000*erf(0.04*x-2.4)
fatalities_function_australia <- function(x) 500+400*erf(0.038*x-3.1)
cases_pre_plot_Australia <- ggplot(australiaPre, aes(x = days, y = total_cases)) + 
    geom_line() + 
    stat_function(fun=cases_function_australia, color="#d33636", size=2, linetype="dotted") +
    scale_x_continuous(breaks = seq(0, minimizedDays, 1)) +
    labs(title = "Total Cases in Australia from 6/1/2020 to 8/9/2020 (70 days)", x = "Days", y = "Total Cases")
fatalities_pre_plot_Australia <- ggplot(australiaPre, aes(x = days, y = total_deaths)) +
    geom_line() + 
    stat_function(fun=fatalities_function_australia, color="#3333e2", size=2, linetype="dotted") +
    scale_x_continuous(breaks = seq(0, minimizedDays, 1)) +
    labs(title = "Total Deaths in Australia from 6/1/2020 to 8/9/2020 (70 days)", x = "Days", y = "Total Deaths")
x <- 0:200
cases_function_australia <- function(x) 17200+10000*erf(0.04*x-2.4)
fatalities_function_australia <- function(x) 500+400*erf(0.038*x-3.1)
cases_plot_Australia <- ggplot(australia, aes(x = days, y = total_cases)) + 
    geom_line() + 
    stat_function(fun=cases_function_australia, color="#d33636", size=1.5) +
    scale_x_continuous(breaks = seq(0, 200, 1)) +
    labs(title = "Total Cases in Australia from 6/1/2020 to 12/18/2020 (200 days)", x = "Days", y = "Total Cases")
fatalities_plot_Australia <- ggplot(australia, aes(x = days, y = total_deaths)) +
    geom_line() + 
    stat_function(fun=fatalities_function_australia, color="#3333e2", size=1.5) +
    scale_x_continuous(breaks = seq(0, 200, 1)) +
    labs(title = "Total Deaths in Australia from 6/1/2020 to 12/18/2020 (200 days)", x = "Days", y = "Total Deaths")
```
```{r, echo=FALSE}
# print(cases_Australia)
# print(fatalities_Australia)
print(cases_pre_plot_Australia)
# print(fatalities_pre_plot_Australia)
# cases_plot_Australia
# print(fatalities_plot_Australia)
```

## Australia results

```{r, echo=FALSE}
# print(cases_Australia)
# print(fatalities_Australia)
# print(cases_pre_plot_Australia)
# print(fatalities_pre_plot_Australia)
cases_plot_Australia
# print(fatalities_plot_Australia)
```

## Italy Simulation

- Add stuff here

## (Fill in Here) Simulation

- Add stuff here

## Works Cited

- Add link to study here
- Add link to covid data here
